Homework 4 - Team 7 (Oisin Harrington, Neal Vaidya, Ozi Boms)
========================================================


### Task 1 - Scraping LQ

<!-- Detail your approach for scraping La Quinta's data -->

```{r}
load("data/dennys.Rdata")
load("data/lq.Rdata")
lq = na.omit(lq)
```


<br/>

## Task 2 - Scraping Denny's

In parse_dennys.R, I drew from the local cache of the Dennys.com site. From that site, I used SelectorGadget and the "fs" package to get all the state codes that are attached to the end of the URL to navigate to a specific state's list of cities. I then used an apply function to create a vector called "cities", which holds the state codes and city names with Denny's to be attached at the end of the URL, or if there is a state with no city list within it because only one city has a Denny's, it just returns the state. Then, drilling down one level further, I used an apply function to find each location within each city (or just the city if there is only one location in the city), and this vector holds the URL to attach at the end of the Dennys.com site for every Denny's location. Then, having the URLs for each location, I saved each of the sites that the URLs point to in my directory under data/dennys.

In parse_dennys.R, I loaded the URLs. The goal in this file was to create a tidy data frame with each row as a Denny's location, and each column as a detail about that Denny's. So, I created a data frame, and created columns for location name, address, and phone number using SelectorGadget and the "fs" package. I fed the raw address into a function to edit addresses and put them in a neat form, to put the address in the form I wanted. For longitude and latitude, I found a Google Maps URL in each location site using developer tools, and the URL contained coordinates. So, I extracted the URL string, and then extracted the coordinates the string, and made a column for longitude and latitude. Then, I saved the tidy data frame in data/.


<br/>

## Task 3 -  Distance Analysis

<!-- Detail your statistical analysis of the pairwise distance between Denny's and LQ's-->

```{r}
library(geosphere)
library(dplyr)

# distHaversine takes location arguments as (longitude, latitude)
dennysloc = cbind(dennys$Longitude, dennys$Latitude) %>% as.matrix()
lqloc = cbind(lq$long, lq$lat) %>% as.matrix()

dist_mat = apply(dennysloc, 1, function(x) distHaversine(x, lqloc, r = 6378.137))

#for each laquinta, which are the closest dennies
closestDennys = apply(dist_mat, 1, min)

#for each dennys, which are the closest laquintas 
closestlq = apply(dist_mat, 2, min)

plot(ecdf(closestlq), do.points = TRUE, xlim=c(-1, 200), main = "Laquintas Closest to Dennys", xlab = "Distance(km)", ylab = "Proportions for each Distance(%)", col="blue") 

plot(ecdf(closestDennys), xlim=c(-1, 200), main = "Dennys Closest to Laquintas", xlab = "Distance(km)", ylab = "Proportions for each Distance(%)", col="red") 

```
